Minimal trap spaces of Boolean networks are maximal siphons of their Petri net encoding

### 2022-12-23 manuscripts/TCS2022/tcs2022.tex
A computational application

% Mention the extensions for the journal version
Herein we extend our previous work in~\cite{DBLP:conf/cmsb/TrinhBHS22} as follows.
First, we showcase one theoretical application of the connection between trap spaces in Boolean networks and conflict-free siphons in Petri nets.
Second, beyond the proposed ASP method, we propose several other possible methods using MaxSAT, CLP, and ILP.
Third, we conduct a more comprehensive benchmark on both real-world and randomly generated models to evaluate all the proposed methods.
Forth, regarding the implementation, we have developed a converter that directly reads a .bnet file and builds the Petri net encoding, instead of using the PNML conversion of BioLQM.
Finally, we explore several complexity analysis on maximal (conflict-free) siphon problems.

@@

  A \emph{siphon} of a Petri net \((P, T, W)\) is a set of places \(S\) such that:
  \[\forall t\in T, S\cap succ(t)\not =\emptyset\Rightarrow S\cap pred(t)\not =\emptyset.\]

@@

Note that \(\emptyset\) is trivially a siphon.

@@

As a computational application, by Theorem~\ref{theo:min_ts_2_max_sp}, we can reduce the problem of computing all minimal trap spaces of a Boolean network to the problem of computing all maximal conflict-free siphons of its Petri net encoding.
Note that in the case of special types of trap spaces (e.g., fixed points), this can be put in regard to special types of siphons in Petri nets.
See Subsection~\ref{subsec:computation_special_ts} for more discussions about many special types of trap spaces.
It might actually be possible to generalize our result to any 1-safe place-complementary Petri net to define a notion of trap spaces that might be useful for the analysis of Petri nets, but this is out of the scope of this article.

@@

First, we show the characterization of all conflict-free siphons of the encoded Petri net \(\mathcal{P} = (P, T, W)\). Suppose that \(S\) is a generic siphon of \(\mathcal{P}\). If a place \(p\) should belong to \(S\), then by definition all the transitions in \(pred(p)\) must belong to \(succ(S)\). Note that \(succ(S) = \bigcup_{p \in S}succ(p)\). A transition \(t\) belongs to \(succ(S)\) if and only if there is at least one place \(p'\) in \(S\) such that \(p' \in pred(t)\). Hence, for each transition \(t \in pred(p)\), we can state that
\begin{equation}
\label{eq:siphon}
p \in S \Rightarrow \bigvee_{p' \in pred(t)}p' \in S.
\end{equation}
The system of all the rules of the above form with respect to all pairs \((p, t)\) where \(p \in P, t \in T, t \in pred(p)\) fully characterizes all generic siphons of a Petri net and has been used with SAT solvers in~\cite{oanea2010new,nabli2016enumerating}.
To make \(S\) to be a conflict-free siphon, we need to add to the system the rule
\begin{equation}
\label{eq:conflict}
p_v \in S \Rightarrow \overline{p_v} \not \in S \wedge \overline{p_v} \in S \Rightarrow p_v \not \in S
\end{equation}for each node \(v \in V\).
By definition, the final system fully characterizes all conflict-free siphons of the encoded Petri net.

@@

@@

\setlength{\tabcolsep}{4pt}
\begin{table}[!htb]
  \caption{Timing comparisons between bioLQM (LQM), PyBoolNet (PBN), mpbn and the four variants of Trappist on the PyBoolNet repository.}
  \centering%
  \label{tab:pyboolnet_repo}
  \begin{tabular}{rlrrrrrrrrr}
    \toprule
    & & & & & & & \multicolumn{4}{c}{Trappist}\\
    \cmidrule(rr){8-11}
    & model & \(n\) & \(|M|\) & LQM & PBN & mpbn & SAT & CLP & ILP & ASP \\
    \rownb & arellano\_rootstem & 9 & 4 & \textbf{0.13} & 0.05 & 0.01 & - & - & - & 0.02\\
    \rownb & calzone\_cellfate & 28 & 27 & \textbf{0.12} & 0.03 & \textbf{NM} & - & - & - & 0.03\\
    \rownb & dahlhaus\_neuroplastoma & 23 & 32 & \textbf{0.11} & 0.05 & 0.02 & - & - & - & 0.03\\
    \rownb & davidich\_yeast & 10 & 12 & \textbf{0.11} & 0.04 & 0.01 & - & - & - & 0.03\\
    \rownb & dinwoodie\_life & 15 & 7 & \textbf{0.11} & 0.03 & 0.01 & - & - & - & 0.03\\
    \rownb & dinwoodie\_stomatal & 13 & 1 & \textbf{0.10} & 0.03 & 0.01 & - & - & - & 0.02\\
    \rownb & faure\_cellcycle & 10 & 2 & \textbf{0.11} & 0.04 & 0.01 & - & - & - & 0.03\\
    \rownb & grieco\_mapk & 53 & 18 & \textbf{0.19} & 0.04 & 0.02 & - & - & - & 0.05\\
    \rownb & irons\_yeast & 18 & 1 & \textbf{0.12} & 0.05 & 0.01 & - & - & - & 0.03\\
    \rownb & jaoude\_thdiff & 103 & $>1000$ & N/A & \textbf{1.44} & \textbf{0.90} & - & - & - & 0.20\\
    \rownb & klamt\_tcr & 40 & 8 & 0.11 & 0.04 & 0.01 & - & - & - & 0.04\\
    \rownb & krumsiek\_myeloid & 11 & 6 & \textbf{0.10} & 0.03 & 0.01 & - & - & - & 0.02\\
    \rownb & multivalued & 13 & 4 & \textbf{0.10} & 0.03 & 0.01 & - & - & - & 0.02\\
    \rownb & n12c5 & 11 & 5 & 0.11 & \textbf{35.16} & 0.01 & - & - & - & 0.04\\
    \rownb & n3s1c1a & 2 & 2 & \textbf{0.10} & 0.02 & 0.01 & - & - & - & 0.02\\
    \rownb & n3s1c1b & 2 & 2 & \textbf{0.09} & 0.02 & 0.01 & - & - & - & 0.01\\
    \rownb & n5s3 & 4 & 3 & \textbf{0.10} & 0.03 & \textbf{NM} & - & - & - & 0.02\\
    \rownb & n6s1c2 & 5 & 3 & \textbf{0.10} & 0.03 & 0.01 & - & - & - & 0.02\\
    \rownb & n7s3 & 6 & 3 & \textbf{0.11} & 0.02 & 0.01 & - & - & - & 0.02\\
    \rownb & raf & 3 & 2 & \textbf{0.10} & 0.02 & 0.01 & - & - & - & 0.02\\
    \rownb & randomnet\_n15k3 & 15 & 3 & 0.10 & 0.03 & \textbf{NM} & - & - & - & 0.04\\
    \rownb & randomnet\_n7k3 & 7 & 10 & \textbf{0.10} & 0.03 & \textbf{NM} & - & - & - & 0.02\\
    \rownb & remy\_tumorigenesis & 34 & 25 & \textbf{0.15} & \textbf{2.14} & 0.02 & - & - & - & 0.06\\
    \rownb & saadatpour\_guardcell & 13 & 1 & \textbf{0.10} & 0.03 & 0.01 & - & - & - & 0.02\\
    \rownb & selvaggio\_emt & 56 & $>1000$ & N/A & \textbf{1.02} & \textbf{0.52} & - & - & - & 0.18\\
    \rownb & tournier\_apoptosis & 12 & 3 & \textbf{0.10} & 0.04 & 0.01 & - & - & - & 0.02\\
    \rownb & xiao\_wnt5a & 7 & 4 & \textbf{0.10} & 0.03 & 0.01 & - & - & - & 0.02\\
    \rownb & zhang\_tlgl & 60 & 156 & \textbf{0.60} & 0.22 & \textbf{NM} & - & - & - & 0.09\\
    \rownb & zhang\_tlgl\_v2 & 60 & 258 & \textbf{0.64} & 0.09 & 0.15 & - & - & - & 0.08\\
    \bottomrule
  \end{tabular}
\end{table}
\setcounter{rownumber}{0}

@@

\begin{table}[!htb]
  \caption{Timing comparisons between bioLQM (LQM), PyBoolNet (PBN), mpbn and the four variants of Trappist on selected models from the literature.}
  \centering%
  \label{tab:result_real}
  \begin{tabular}{rlrrrrrrrrr}
    \toprule
    & & & & & & & \multicolumn{4}{c}{Trappist}\\
    \cmidrule(rr){8-11}
    & model & \(n\) & \(|M|\) & LQM & PBN & mpbn & SAT & CLP & ILP & ASP \\
    \midrule % n < 100
    \rownb & Arabidopsis\_thaliana~\cite{DesignPrinciplesGeneNetworks} & 15 & 8 & 0.15 & - & - & - & - & - & - \\
    \rownb & Bcell~\cite{Dutta2019} & 73 & 72 & 0.21 & - & - & - & - & - & - \\
    \rownb & Cacace\_TdevModel~\cite{Cacace2020} & 61 & 28 & 1.21 & - & NM & - & - & - & - \\
    \rownb & Corral\_ThIL17diff~\cite{corral2021interplay} & 92 & - & N/A & - & - & - & - & - & - \\
    \rownb & DNA\_damage~\cite{DesignPrinciplesGeneNetworks} & 26 & - & 0.23 & - & NM & - & - & - & - \\
    \rownb & Drosophila~\cite{RodrguezVega2014} & 52 & - & 0.33 & - & - & - & - & - & - \\
    \rownb & EMT~\cite{Rozum2021} & 69 & - & - & - & - & - & - & - & - \\
    \rownb & mast\_cell~\cite{aghamiri2020automated} & 73 & - & N/A & - & - & - & - & - & - \\
    \rownb & FT-GRN~\cite{ChvezHernndez2022} & 23 & - & DNF & - & NM & - & - & - & - \\
    \rownb & hedgehog~\cite{DesignPrinciplesGeneNetworks} & 65 & - & N/A & - & - & - & - & - & - \\
    \rownb & metastatic~\cite{DesignPrinciplesGeneNetworks} & 10 & - & 0.11 & - & NM & - & - & - & - \\
    \rownb & Pancreatic\_Cancer~\cite{DesignPrinciplesGeneNetworks} & 43 & - & N/A & - & - & - & - & - & - \\
    \rownb & Pluripotent~\cite{DesignPrinciplesGeneNetworks} & 36 & - & 0.37 & - & NM & - & - & - & - \\
    \rownb & Rho-GTPases~\cite{DesignPrinciplesGeneNetworks} & 33 & 1 & 0.21 & - & - & - & - & - & - \\
    \rownb & Pluripotency~\cite{YachieKinoshita2018} & 36 & - & DNF & - & NM & - & - & - & - \\
    \rownb & p53\_high\_dna~\cite{DesignPrinciplesGeneNetworks} & 16 & 1 & 0.40 & - & NM & - & - & - & - \\
    \rownb & p53\_low\_dna~\cite{DesignPrinciplesGeneNetworks} & 16 & 1 & 0.38 & - & NM & - & - & - & - \\

    \midrule % 100 <= n < 200
    \rownb & angiofull~\cite{Weinstein2017} & 142 & - & N/A & - & - & - & - & - & - \\
    %\rownb & COVID\_19 & 111 & - & N/A & - & - & - & - & - & - \\
    \rownb & EMT\_Mech~\cite{Sullivan2022} & 136 & - & DNF & - & - & - & - & - & - \\
    \rownb & EMT\_Mech\_TGFbeta~\cite{Sullivan2022} & 150 & - & DNF & - & - & - & - & - & - \\
    \rownb & MAPK~\cite{aghamiri2020automated} & 181 & - & N/A & - & - & - & - & - & - \\
    \rownb & macrophage~\cite{DesignPrinciplesGeneNetworks} & 136 & - & N/A & - & - & - & - & - & - \\
    \rownb & RA\_apoptosis~\cite{aghamiri2020automated} & 180 & - & N/A & - & - & - & - & - & - \\
    \rownb & Adhesion\_CIP~\cite{guberman2020boolean} & 121 & - & 57.33 & - & - & - & - & - & - \\
    \rownb & angiogenesis~\cite{DesignPrinciplesGeneNetworks} & 141 & - & N/A & - & - & - & - & - & - \\

    \midrule % 200 <= n
    \rownb & T-cell-co-receptor~\cite{DesignPrinciplesGeneNetworks} & 206 & - & N/A & - & - & - & - & - & - \\
    \rownb & Snf1-pathway~\cite{Lubitz2015} & 202 & - & N/A & - & - & - & - & - & - \\
    \rownb & Mycobacterium~\cite{DesignPrinciplesGeneNetworks} & 317 & - & N/A & - & - & - & - & - & - \\
    \rownb & Leishmania~\cite{DesignPrinciplesGeneNetworks} & 342 & - & N/A & - & - & - & - & - & - \\
    \rownb & TcellCheckPoint~\cite{hernandez2020computational} & 218 & - & N/A & - & NM & - & - & - & - \\
    \rownb & Cholocystokinin~\cite{aghamiri2020automated} & 383 & - & N/A & - & - & - & - & - & - \\
    \rownb & Alzheimer~\cite{aghamiri2020automated} & 762 & - & N/A & - & NM & - & - & - & - \\

@@

\begin{table}[!htb]
  \caption{Results on N-K models.}
  \centering%
  \label{tab:result_N_K}
  \begin{tabular}{rrrrrrrr}
    \toprule
    & & & & \multicolumn{4}{c}{Trappist}\\
    \cmidrule(rr){5-8}
    \(n\) & LQM & mpbn & PBN & maxSAT & CLP & ILP & ASP \\
    \midrule
    100 & - & - & - & - & - & - & - \\
    150 & - & - & - & - & - & - & - \\
    200 & - & - & - & - & - & - & - \\
    250 & - & - & - & - & - & - & - \\
    300 & - & - & - & - & - & - & - \\
    350 & - & - & - & - & - & - & - \\
    400 & - & - & - & - & - & - & - \\
    \bottomrule
  \end{tabular}
\end{table}

\begin{table}[!htb]
  \caption{Results on scale-free models.}
  \centering%
  \label{tab:result_scale_free}
  \begin{tabular}{rrrrrrrr}
    \toprule
    & & & & \multicolumn{4}{c}{Trappist}\\
    \cmidrule(rr){5-8}
    \(n\) & LQM & mpbn & PBN & maxSAT & CLP & ILP & ASP \\
    \midrule
    500 & - & - & - & - & - & - & - \\
    750 & - & - & - & - & - & - & - \\
    1000 & - & - & - & - & - & - & - \\
    1250 & - & - & - & - & - & - & - \\
    1500 & - & - & - & - & - & - & - \\
    1750 & - & - & - & - & - & - & - \\
    2000 & - & - & - & - & - & - & - \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

% Mention the extensions for the journal version
Herein we extend our previous work in~\cite{DBLP:conf/cmsb/TrinhBHS22} as follows.
First, we showcase one theoretical application of the connection between trap spaces in Boolean networks and conflict-free siphons in Petri nets.
Second, beyond the proposed ASP method, we propose several other possible methods for computing minimal trap spaces using MaxSAT, CLP, and ILP.
Third, we discuss in detail how to compute several special types of trap space in a Boolean network.
Forth, regarding the implementation, we have developed a converter that directly reads a .bnet file and builds the Petri net encoding, instead of using the PNML conversion of BioLQM.
%Finally, we explore several complexity analysis on maximal (conflict-free) siphon problems.
Finally, we conduct a more comprehensive benchmark on both real-world and randomly generated models to evaluate all the proposed methods.

@@

  A \emph{siphon} of a Petri net \((P, T, W)\) is a set of places \(S\) such that:
  \[\forall t\in T, S\cap succ(t)\not =\emptyset\Rightarrow S\cap pred(t)\not =\emptyset.\]
  Note that \(\emptyset\) is trivially a siphon.

@@

Let \(pred(S) := \bigcup_{s \in S}pred(s)\) and \(succ(S) := \bigcup_{s \in S}succ(s)\).
We have an important property~\cite{DBLP:journals/isci/LiuB16} as follows.

\begin{proposition}
\label{prop:siphon_set}
  Let \(S\) be a siphon of a Petri net \((P, T, W)\).
  Then \(pred(S) \subseteq succ(S)\).

@@

One naturally computational application of Theorem~\ref{theo:ts_2_sp} is that we can efficiently decide whether a subspace \(m\) is a trap space.
In PyBoolNet~\cite{klarner2017pyboolnet}, this is checked by using the percolation on the prime-implicants of the Boolean functions.
As we have mentioned at the beginning of this article, there may be a huge number of prime-implicants.
Hence, the checking method in~\cite{klarner2017pyboolnet} shows its limitations.
Instead, we can first compute the mirror \(S_m\) of \(m\) in the Petri net encoding.
Then, by Proposition~\ref{prop:siphon_set} and Theorem~\ref{theo:ts_2_sp}, we check if \(pred(S_m) \subseteq succ(S_m)\).
Note that the above computation (also the Petri net construction) is linear in the number of transitions of the Petri net, which can be much smaller than the number of prime-implicants~\cite{chatain2014characterization}.

Furthermore, by Theorem~\ref{theo:min_ts_2_max_sp}, we can reduce the problem of computing all minimal trap spaces of a Boolean network to the problem of computing all maximal conflict-free siphons of its Petri net encoding.
Note that in the case of special types of trap spaces (e.g., fixed points), this can be put in regard to special types of siphons in Petri nets.
See Subsection~\ref{subsec:computation_special_ts} for more discussions about many special types of trap spaces.
It might actually be possible to generalize our result to any 1-safe place-complementary Petri net to define a notion of trap spaces that might be useful for the analysis of Petri nets, but this is out of the scope of this article.

@@

First, we show the characterization of all conflict-free siphons of the encoded Petri net \(\mathcal{P} = (P, T, W)\).
Suppose that \(S\) is a generic siphon of \(\mathcal{P}\). If a place \(p\) should belong to \(S\), then by Proposition~\ref{prop:siphon_set} all the transitions in \(pred(p)\) must belong to \(succ(S)\).
Note that \(succ(S) = \bigcup_{p \in S}succ(p)\).
A transition \(t\) belongs to \(succ(S)\) if and only if there is at least one place \(p'\) in \(S\) such that \(p' \in pred(t)\).
Hence, for each transition \(t \in pred(p)\), we can state that
\begin{equation}
\label{eq:siphon}
p \in S \Rightarrow \bigvee_{p' \in pred(t)}p' \in S.
\end{equation}
The system of all the rules of the above form with respect to all pairs \((p, t)\) where \(p \in P, t \in T, t \in pred(p)\) fully characterizes all generic siphons of a Petri net and has been used with SAT solvers in~\cite{oanea2010new,nabli2016enumerating}.
To make \(S\) to be a conflict-free siphon, we need to add to the system the rule
\begin{equation}
\label{eq:conflict}
p_v \in S \Rightarrow \overline{p_v} \not \in S \wedge \overline{p_v} \in S \Rightarrow p_v \not \in S
\end{equation}for each node \(v \in V\).
By definition, the final system fully characterizes all conflict-free siphons of the encoded Petri net.

@@

In the field of systems biology, biologists may want to compute more special types of trap spaces beyond minimal trap spaces~\cite{klarner2017pyboolnet}.
We shall show that our proposed methods can be easily adjusted to compute popular types of trap spaces.
We illustrate the adjustments via the ASP-based method (see Subsection~\ref{subsec:computation_asp}), but these adjustments are completely applicable for other approaches such as MaxSAT, CSP, and ILP.

First, maximal trap spaces // TODO:

Second, fixed points // TODO:

Third, trap spaces inside a subspace // TODO:

Finally, trap spaces that intersect a subspace // TODO:

@@

\setlength{\tabcolsep}{4pt}
\begin{table}[!htb]
  \caption{Timing comparisons between bioLQM (LQM), PyBoolNet (PBN), mpbn and the four variants of Trappist on the PyBoolNet repository.}
  \centering%
  \label{tab:pyboolnet_repo}
  \begin{tabular}{rlrrrrrrrrr}
    \toprule
    & & & & & & & \multicolumn{4}{c}{Trappist}\\
    \cmidrule(rr){8-11}
    & model & \(n\) & \(|M|\) & LQM & PBN & mpbn & SAT & CLP & ILP & ASP \\
    \rownb & arellano\_rootstem & 9 & 4 & \textbf{0.13} & 0.05 & - & - & - & - & 0.02\\
    \rownb & calzone\_cellfate & 28 & 27 & \textbf{0.12} & 0.03 & - & - & - & - & 0.03\\
    \rownb & dahlhaus\_neuroplastoma & 23 & 32 & \textbf{0.11} & 0.06 & - & - & - & - & 0.03\\
    \rownb & davidich\_yeast & 10 & 12 & \textbf{0.11} & 0.04 & - & - & - & - & 0.04\\
    \rownb & dinwoodie\_life & 15 & 7 & \textbf{0.11} & 0.03 & - & - & - & - & 0.03\\
    \rownb & dinwoodie\_stomatal & 13 & 1 & \textbf{0.10} & 0.03 & - & - & - & - & 0.02\\
    \rownb & faure\_cellcycle & 10 & 2 & \textbf{0.11} & 0.04 & - & - & - & - & 0.05\\
    \rownb & grieco\_mapk & 53 & 18 & \textbf{0.19} & 0.04 & - & - & - & - & 0.06\\
    \rownb & irons\_yeast & 18 & 1 & \textbf{0.12} & 0.05 & - & - & - & - & 0.06\\
    \rownb & jaoude\_thdiff & 103 & $>1000$ & N/A & \textbf{1.92} & - & - & - & - & 0.20\\
    \rownb & klamt\_tcr & 40 & 8 & 0.11 & 0.04 & - & - & - & - & 0.04\\
    \rownb & krumsiek\_myeloid & 11 & 6 & \textbf{0.10} & 0.03 & - & - & - & - & 0.02\\
    \rownb & multivalued & 13 & 4 & \textbf{0.10} & 0.03 & - & - & - & - & 0.02\\
    \rownb & n12c5 & 11 & 5 & 0.11 & \textbf{38.80} & - & - & - & - & 0.04\\
    \rownb & n3s1c1a & 2 & 2 & \textbf{0.10} & 0.02 & - & - & - & - & 0.02\\
    \rownb & n3s1c1b & 2 & 2 & \textbf{0.09} & 0.02 & - & - & - & - & 0.01\\
    \rownb & n5s3 & 4 & 3 & \textbf{0.10} & 0.03 & \textbf{NM} & - & - & - & 0.02\\
    \rownb & n6s1c2 & 5 & 3 & \textbf{0.10} & 0.04 & - & - & - & - & 0.02\\
    \rownb & n7s3 & 6 & 3 & \textbf{0.11} & 0.02 & - & - & - & - & 0.02\\
    \rownb & raf & 3 & 2 & \textbf{0.10} & 0.02 & - & - & - & - & 0.02\\
    \rownb & randomnet\_n15k3 & 15 & 3 & 0.10 & 0.04 & \textbf{NM} & - & - & - & 0.04\\
    \rownb & randomnet\_n7k3 & 7 & 10 & \textbf{0.10} & 0.03 & \textbf{NM} & - & - & - & 0.02\\
    \rownb & remy\_tumorigenesis & 34 & 25 & \textbf{0.15} & \textbf{2.05} & - & - & - & - & 0.06\\
    \rownb & saadatpour\_guardcell & 13 & 1 & \textbf{0.10} & 0.02 & - & - & - & - & 0.02\\
    \rownb & selvaggio\_emt & 56 & $>1000$ & N/A & \textbf{1.09} & - & - & - & - & 0.18\\
    \rownb & tournier\_apoptosis & 12 & 3 & \textbf{0.10} & 0.03 & - & - & - & - & 0.02\\
    \rownb & xiao\_wnt5a & 7 & 4 & \textbf{0.10} & 0.02 & - & - & - & - & 0.02\\
    \rownb & zhang\_tlgl & 60 & 156 & \textbf{0.60} & 0.22 & - & - & - & - & 0.09\\
    \rownb & zhang\_tlgl\_v2 & 60 & 258 & \textbf{0.64} & 0.11 & - & - & - & - & 0.08\\
    \bottomrule
  \end{tabular}
\end{table}
\setcounter{rownumber}{0}

@@

\begin{table}[!htb]
  \caption{Timing comparisons between bioLQM (LQM), PyBoolNet (PBN), mpbn and the four variants of Trappist on selected models from the literature.}
  \centering%
  \label{tab:result_real}
  \begin{tabular}{rlrrrrrrrrr}
    \toprule
    & & & & & & & \multicolumn{4}{c}{Trappist}\\
    \cmidrule(rr){8-11}
    & model & \(n\) & \(|M|\) & LQM & PBN & mpbn & SAT & CLP & ILP & ASP \\
    \midrule % n < 100
    \rownb & Arabidopsis\_thaliana~\cite{DesignPrinciplesGeneNetworks} & 15 & 8 & 0.15 & - & NM & - & - & - & - \\
    \rownb & Bcell~\cite{Dutta2019} & 73 & 72 & 0.21 & - & - & - & - & - & - \\
    \rownb & Cacace\_TdevModel~\cite{Cacace2020} & 61 & 28 & 1.21 & - & NM & - & - & - & - \\
    \rownb & Corral\_ThIL17diff~\cite{corral2021interplay} & 92 & $>1000$ & N/A & - & - & - & - & - & - \\
    \rownb & DNA\_damage~\cite{DesignPrinciplesGeneNetworks} & 26 & 16 & 0.23 & - & NM & - & - & - & - \\
    \rownb & Drosophila~\cite{RodrguezVega2014} & 52 & 128 & 0.33 & - & - & - & - & - & - \\
    \rownb & EMT~\cite{Rozum2021} & 69 & 268 & - & - & - & - & - & - & - \\
    \rownb & mast\_cell~\cite{aghamiri2020automated} & 73 & $>1000$ & N/A & - & - & - & - & - & - \\
    \rownb & FT-GRN~\cite{ChvezHernndez2022} & 23 & 32 & DNF & - & NM & - & - & - & - \\
    \rownb & hedgehog~\cite{DesignPrinciplesGeneNetworks} & 65 & $>1000$ & N/A & - & - & - & - & - & - \\
    \rownb & metastatic~\cite{DesignPrinciplesGeneNetworks} & 10 & 4 & 0.11 & - & NM & - & - & - & - \\
    \rownb & Pancreatic\_Cancer~\cite{DesignPrinciplesGeneNetworks} & 43 & $>1000$ & N/A & - & - & - & - & - & - \\
    \rownb & Pluripotent~\cite{DesignPrinciplesGeneNetworks} & 36 & 276 & 0.37 & - & NM & - & - & - & - \\
    \rownb & Rho-GTPases~\cite{DesignPrinciplesGeneNetworks} & 33 & 2 & 0.21 & - & - & - & - & - & - \\
    \rownb & Pluripotency~\cite{YachieKinoshita2018} & 36 & 440 & DNF & - & NM & - & - & - & - \\
    \rownb & p53\_high\_dna~\cite{DesignPrinciplesGeneNetworks} & 16 & 1 & 0.40 & - & NM & - & - & - & - \\
    \rownb & p53\_low\_dna~\cite{DesignPrinciplesGeneNetworks} & 16 & 1 & 0.38 & - & NM & - & - & - & - \\

    \midrule % 100 <= n < 200
    \rownb & angiofull~\cite{Weinstein2017} & 142 & $>1000$ & N/A & - & - & - & - & - & - \\
    %\rownb & COVID\_19 & 111 & - & N/A & - & - & - & - & - & - \\
    \rownb & EMT\_Mech~\cite{Sullivan2022} & 136 & 82 & DNF & - & - & - & - & - & - \\
    \rownb & EMT\_Mech\_TGFbeta~\cite{Sullivan2022} & 150 & 492 & DNF & - & - & - & - & - & - \\
    \rownb & MAPK~\cite{aghamiri2020automated} & 181 & $>1000$ & N/A & - & - & - & - & - & - \\
    \rownb & macrophage~\cite{DesignPrinciplesGeneNetworks} & 136 & $>1000$ & N/A & - & - & - & - & - & - \\
    \rownb & RA\_apoptosis~\cite{aghamiri2020automated} & 180 & $>1000$ & N/A & - & - & - & - & - & - \\
    \rownb & Adhesion\_CIP~\cite{guberman2020boolean} & 121 & 78 & 57.33 & - & - & - & - & - & - \\
    \rownb & angiogenesis~\cite{DesignPrinciplesGeneNetworks} & 141 & $>1000$ & N/A & - & - & - & - & - & - \\

    \midrule % 200 <= n
    \rownb & T-cell-co-receptor~\cite{DesignPrinciplesGeneNetworks} & 206 & $>1000$ & N/A & - & - & - & - & - & - \\
    \rownb & Snf1-pathway~\cite{Lubitz2015} & 202 & $>1000$ & N/A & - & - & - & - & - & - \\
    \rownb & Mycobacterium~\cite{DesignPrinciplesGeneNetworks} & 317 & $>1000$ & N/A & - & - & - & - & - & - \\
    \rownb & Leishmania~\cite{DesignPrinciplesGeneNetworks} & 342 & $>1000$ & N/A & - & - & - & - & - & - \\
    \rownb & TcellCheckPoint~\cite{hernandez2020computational} & 218 & $>1000$ & N/A & - & NM & - & - & - & - \\
    \rownb & Cholocystokinin~\cite{aghamiri2020automated} & 383 & $>1000$ & N/A & - & - & - & - & - & - \\
    \rownb & Alzheimer~\cite{aghamiri2020automated} & 762 & $>1000$ & N/A & - & NM & - & - & - & - \\

@@

\begin{table}[!htb]
  \caption{Results on N-K models.}
  \centering%
  \label{tab:result_N_K}
  \begin{tabular}{rrrrrrrr}
    \toprule
    & & & & \multicolumn{4}{c}{Trappist}\\
    \cmidrule(rr){5-8}
    \(n\) & LQM & mpbn & PBN & maxSAT & CLP & ILP & ASP \\
    \midrule
    100 & 50-50-50 & 50-50-50 & - & - & - & - & - \\
    150 & 50-50-50 & 50-50-50 & - & - & - & - & - \\
    200 & 50-50-50 & 50-50-50 & - & - & - & - & - \\
    250 & 50-50-50 & 50-50-50 & - & - & - & - & - \\
    300 & 50-50-50 & 50-50-50 & - & - & - & - & - \\
    350 & 50-50-50 & 50-50-50 & - & - & - & - & - \\
    400 & 50-50-50 & 50-50-50 & - & - & - & - & - \\
    \bottomrule
  \end{tabular}
\end{table}

\begin{table}[!htb]
  \caption{Results on scale-free models.}
  \centering%
  \label{tab:result_scale_free}
  \begin{tabular}{rrrrrrrr}
    \toprule
    & & & & \multicolumn{4}{c}{Trappist}\\
    \cmidrule(rr){5-8}
    \(n\) & LQM & mpbn & PBN & maxSAT & CLP & ILP & ASP \\
    \midrule
    500 & 50-50-50 & 50-50-50 & - & - & - & - & - \\
    750 & 50-50-50 & 50-50-50 & - & - & - & - & - \\
    1000 & 50-50-50 & 50-50-50 & - & - & - & - & - \\
    1250 & 50-50-50 & 50-50-50 & - & - & - & - & - \\
    1500 & 50-50-50 & 50-50-50 & - & - & - & - & - \\
    1750 & 50-50-50 & 50-50-50 & - & - & - & - & - \\
    2000 & 50-50-50 & 50-50-50 & - & - & - & - & - \\
    \bottomrule
  \end{tabular}
\end{table}
